---
title: "Exploratory analysing on World Happiness Report - Modelling"
author: "Weihao Li"
email: "wlii0039@student.monash.edu"
date: "9th June 2020"
pdflink: ""
bgimg: "images/8McqxSj.jpg"
output:
  xaringan::moon_reader:
    css:
      - ninjutsu 
      - "assets/animate.css"
      - "assets/monash-logo.css"
      - "assets/monash-brand.css"
      - "assets/monash-fonts.css"
      - "assets/styles.css" # small improvements
      - "assets/custom.css" # add your own CSS here!
    self_contained: false 
    seal: false 
    chakra: 'libs/remark-latest.min.js'
    lib_dir: libs
    includes:
      in_header: "assets/custom.html"
    mathjax: "assets/mathjax-local/MathJax.js?config=TeX-AMS-MML_HTMLorMML"
    nature:
      highlightStyle: github 
      highlightLanguage: r 
      highlightLines: true
      highlightSpans: false 
      countIncrementalSlides: false
      slideNumberFormat: '%current%/%total%'
      navigation:
        scroll: false 
        touch: true
        click: false
      ratio: '16:9'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
```

```{r titleslide, child="components/titleslide.Rmd"}
```

---
#My work

.grid[

.font_my_2[

##Initialization


1. Initialize the remote repostory on Github
2. Push the EBS report template and datasets to the remote repo

##Help

3. Fix issues
  - .bib file
  - cross-refences syntax
  - plots labels
4. Format the final report

]

.font_my_2[

##Modelling

3. Find an issue with the happiness data that the explantory variables are useless for modelling
4. Join other data from the world bank
5. Build a classical linear model to explain the happiness score
6. Interpretation
7. Potential issues disscussion 
  - Endogeneity
  - Sample selection
8. Regression diagnostic
  - Nomality
  - Heteroskedasticity
  - Leverage



]
]
---
# Tools
## R Markdown
- Template: MonashEBSTemplates (https://github.com/robjhyndman/MonashEBSTemplates)

## Version Control
- Git bash
  - almost everything
- Gitraken
  - Stage file
  - View tree diagram
  - Check project progress in Boards


---

## Figure source

- On the banks of the Yarra - https://i.imgur.com/8McqxSj.jpg

---
```{r endslide, child="components/endslide.Rmd"}
```


