---
title: "Exploratory analysing on World Happiness Report"
author:
- familyname: Li
  othernames: Weihao
  address: Monash University
  email: wlii0039@student.monash.edu
  correspondingauthor: true
  qualifications: 28723740
- familyname: Curie
  othernames: Pierre
  address: University of Paris
  qualifications: Nobel Prize, PhD
department: Department of\newline Econometrics &\newline Business Statistics
organization: ETC5513 Assignment 4
bibliography: references.bib
biblio-style: apa
linestretch: 1.5
output:
  MonashEBSTemplates::report:
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    includes:
      in_header: preamble.tex
    keep_tex: yes
    number_sections: yes
    citation_package: biblatex
    toc: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache=FALSE, messages=FALSE, warning=FALSE)
# Make sure you have the latest versions of rmarkdown and bookdown installed
library(tidyverse)

```


# Q4. What is the relationship between predictors and happiness score in a linear regression analysis?



```{r message=FALSE}
h15 = read_csv("Data/2015.csv")
h16 = read_csv("Data/2016.csv")
h17 = read_csv("Data/2017.csv")
h18 = read_csv("Data/2018.csv")
h18$`Perceptions of corruption` = as.numeric(h18$`Perceptions of corruption`)
h19 = read_csv("Data/2019.csv")
```

<!--

```{r}
mod15 = lm(as.formula(paste('`', 
                            colnames(h15)[4], "`~`",
                            paste(colnames(h15)[c(6, 7, 8, 9, 10, 11, 12)], collapse = "`+`"),
                            '`',
        sep = ""
    )), data = h15)
```

```{r mod2015}
c_table = summary(mod15)

rownames(c_table$coefficients) = c_table$coefficients %>%
  rownames() %>%
  stringr::str_remove_all('`')

c_table$coefficients %>%
  knitr::kable('latex', 
               digits = 4, 
               booktabs = TRUE,
               caption = "Linear regression model for happiness scores in 2015. The $R^2$ of this model is 1. In the dataset, these factors are standardized.") %>%
  kableExtra::kable_styling(latex_options = "striped")
```


To explore the relationship between hapiness score and factors including economy, family, health, freedom, trust and generosity, a linear regression model for the 2015 data was developed. Results of this model is shown in Table \ref{tab:mod2015}. From the result, we can conclude the estimated closed form of hapiness score:

\begin{align*}
\text{Hapiness score} = & \text{ GDP per Capita } + \text{ Family } + \text{ Life expectancy }+ \text{ Freedom } +   \\ 
&  \text{ Government Corruption } + \text{ Generosity } + \text{Dystopia Residual }
\end{align*}

There is strong evidence that the happiness score is and only is a simple average of these factors. Therefore, the relationship between happiness score and these factors is no longer interesting to us.

This situation also happens in 2016 and 2017 data. Besides, for 2018 and 2019 data, the organization provides another set of variables which are also highly correlated with the happiness score, but we have no method to understand what those values represent since they have been transformed in an unknown manner.

Instead of using the factors in the given dataset, we join other datasets to analysis the happiness score, including GDP, CPI, population and area by country. GDP, CPI and population data is downloaded from The World Bank. And area of each country is computed using the simple feature polygons provided in package `rnaturalearth`.

-->

```{r message=FALSE, warning=FALSE}
library(rnaturalearth)
library(sf)
world_map = ne_countries(returnclass = 'sf')
gdp = read_csv("Data/API_NY.GDP.MKTP.CD_DS2_en_csv_v2_1120928.csv", skip = 4)
cpi = read_csv("Data/API_FP.CPI.TOTL.ZG_DS2_en_csv_v2_1120899.csv", skip = 4)
population = read_csv("Data/API_SP.POP.TOTL_DS2_en_csv_v2_1120881.csv", skip = 4)
```

```{r}
temp = h15 %>%
  select(Country, `Happiness Score`) %>%
  mutate(year = 2015)

h16 %>%
  select(Country, `Happiness Score`) %>%
  mutate(year = 2016) %>%
  rbind(temp) -> temp

h17 %>%
  select(Country, `Happiness Score` = Happiness.Score) %>%
  mutate(year = 2017) %>%
  rbind(temp) -> temp

h18 %>%
  select(Country = `Country or region`, `Happiness Score` = Score) %>%
  mutate(year = 2018) %>%
  rbind(temp) -> temp

h19 %>%
  select(Country = `Country or region`, `Happiness Score` = Score) %>%
  mutate(year = 2019) %>%
  rbind(temp) -> temp
```

```{r}
hs = temp
```

```{r message=FALSE}
population %>%
  select(Country = `Country Name`, `2015`:`2019`) %>%
  gather(key = 'year', value = 'population', `2015`:`2019`) %>%
  mutate(year = as.numeric(year)) %>%
  right_join(hs) -> hs

gdp %>%
  select(Country = `Country Name`, `2015`:`2019`) %>%
  gather(key = 'year', value = 'gdp', `2015`:`2019`) %>%
  mutate(year = as.numeric(year)) %>%
  right_join(hs) -> hs

cpi %>%
  select(Country = `Country Name`, `2015`:`2019`) %>%
  gather(key = 'year', value = 'cpi', `2015`:`2019`) %>%
  mutate(year = as.numeric(year)) %>%
  right_join(hs) -> hs
```

```{r warning=FALSE, message=FALSE}
world_map$area = st_area(world_map) %>% as.numeric()

as_tibble(world_map) %>%
  select(area, name) %>%
  right_join(hs, by = c('name' = 'Country')) -> hs

```

```{r }
nona_hs = na.omit(hs)

nona_hs = nona_hs %>%
  mutate(log_score = log(`Happiness Score`), log_gdp = log(gdp), log_area = log(area), log_population = log(population)) %>%
  select(log_score:log_population, name, year, cpi)

lm(log_score~cpi+log_gdp+log_population+log_area,data=nona_hs) %>%
  summary() -> lm_sum

```


We use variables mentioned in Q3 as predictors, the regression result is shown in Table \ref{tab:lmcoeff}. According to the result, we can write down the formula for this model:

```{r lmcoeff}

rownames(lm_sum$coefficients) = lm_sum$coefficients %>%
  rownames() %>%
  stringr::str_remove_all('`')

lm_sum$coefficients %>%
  knitr::kable('latex', 
               digits = 4, 
               booktabs = TRUE,
               caption = "Linear regression model for happiness scores. The $R^2$ of this model is 0.7264.") %>%
  kableExtra::kable_styling(latex_options = "striped")
```

\begin{align*}
\text{log(Happiness Score)} = & \ 0.3208 + 0.0005\text{ CPI} + 0.1285 \text{ log(GDP)} \\
&- 0.1218 \text{ log(Population)} + 0.0056 \text{ log(Area)}
\end{align*}

Notice that only the intercept, log of GDP and the log of the population are significant with $\alpha = 5$%. Since we take logarithm on both response variable and regressors except CPI given it is a percentage index, we can interpret them as the elasticity of happiness score of GDP and the elasticity of happiness score of the population. This can be proved by:

\begin{align}
\frac{\partial \text{log(Happiness Score)}}{\partial \text{log(GDP)}} &= 0.1285\\
\intertext{From (1) we can say, when other variables remain constant }\nonumber \\
\Delta \text{ log(Happiness Score)} &= 0.1285 \Delta \text{ log(GDP)}\\
\intertext{By using the linear approximation of log function, we can know}\nonumber\\
log(x_0 + \Delta x) - log(x_0) &\approx log(x_0) + log'(x_0)\Delta x - log(x_0)\\
&=  \frac{\Delta x}{x_0} = \text{percentage change in x}\nonumber\\
\intertext{Therefore}\nonumber\\
\frac{\Delta \text{ log(Happiness Score)}}{\Delta \text{ log(GDP)}} &\approx \frac{\Delta \text{ Happiness Score}}{\Delta \text{ GDP} }\frac{\text{GDP}}{\text{Happiness Score}}\\
&=\frac{\% \Delta \text{ Happiness Score}}{\% \Delta \text{ GDP}} \nonumber\\
&= 0.1285\nonumber
\end{align}

Now we can interpret the result from Table \ref{tab:lmcoeff}. Only variables that are statistically significant will be reported. Roughly, a 1% increase in GDP leads to a 0.1285% rise in the happiness score, and a 1% increase in population leads to a 0.1218% fall in the happiness score.

```{r}
world_map$not_included = is.na(sapply(world_map$name, match, table = hs$name))
```

```{r namap, fig.cap="The world map of missing countries in our dataset"}
ggplot()+
  geom_sf(data = world_map, aes(fill = not_included))+
  ggtitle("World map of countries that are not included in our dataset") +
  theme_bw()+
  theme(legend.position = 'bottom') +
  labs(fill = "Not included")
```


Apparently, the happiness score can be affected by other factors that correlated with regressors and doesn't include in our model, such as the education index and the social welfare system. It means an endogeneity issue occurs in our model, which leads our estimator to be bias and inconsistent. We can either include other variables that we think will be useful for happiness score prediction, or find instrumental variable and fit a Two-Stage least squares regression. Besides, another issue with our model is the sample selection problem. There are only 126 countries with completed cases in our final dataset, which means 69 countries are not considered. Figure \ref{fig:namap} shows the map of missing countries. According to the map, most of the countries being omitted are developing countries. It indicates that our samples are not randomly selected from the population, and we are facing an observability issue. It can be expected that the happiness scores in those countries are lower than the average, which suggests we potentially underestimate our coefficients in OLS. 

The diagnostics of our regression is shown in Figure \ref{fig:dig}. From the Residuals vs Fitted plot, we can see the non-constant variance across the fitted value. The model can be adjusted using Heteroskedasticity and Autocorrelation Consistent (HAC) covariance matrix estimation to let our inference to be credible. The QQ plot suggests the density of residuals is asymmetric, but it is very close to a normal distribution. In the Cooks distances vs Fitted plot, we use 4/(n-k-1) as the threshold. The most influential points are from Suriname, Angola, Botswana, Sudan, Gabon, Sierra Leone, Togo and Burundi. Figure \ref{fig:ip} shows the pattern of these countries. Most of them are in Africa, which contains extreme values in either happiness scores, GDP, CPI or area. It tells us that Africa is different from other places in the world, and we can consider putting a dummy variable in our model to indicate whether the country is in Africa.

In conclusion, this model does a solid job in explaining the relationship between happiness score and our regressors if our point of interest is countries outside Africa. 






```{r dig, fig.cap="Regression diagnostics for checking heteroskedasticity, non-normality and influential points", message=FALSE, fig.height=10}
library(ggrepel)
mod = lm(log_score~cpi+log_gdp+log_population+log_area,data=nona_hs)

mod_detail = broom::augment(mod, data = nona_hs)
p1 = ggplot(mod_detail) +
  geom_point(aes(.fitted, .resid)) +
  geom_smooth(aes(.fitted, .resid))

p2 = ggplot(mod_detail) +
  geom_qq(aes(sample = .resid)) +
  geom_qq_line(aes(sample = .resid))

p3 = ggplot(mod_detail) +
  geom_point(aes(.fitted, .cooksd)) +
  geom_text_repel(data = filter(mod_detail, .cooksd>0.0083), aes(.fitted, .cooksd, label = paste0(name,',',year)), col = 'red') +
  geom_point(data = filter(mod_detail, .cooksd>0.0083), aes(.fitted, .cooksd), col="blue")

library(gridExtra)
grid.arrange(arrangeGrob(p1,p2, ncol=2),
         arrangeGrob(p3, ncol=1, nrow=1), top = "Regression diagnostics\n Top left: Residuals vs Fitted. Top right: Normal QQ plot. Bottom:  Cooks distances vs Fitted.", heights=c(1,2))
```


```{r ip, fig.cap="Diagnostics for influential data points", fig.height=10}
p1 = ggplot()+
  geom_sf(data = world_map, aes(fill = name %in% c('Suriname', 'Angola', 'Botswana', 'Sudan', 'Gabon', 'Sierra Leone', 'Togo', 'Burundi'))) +
  theme_bw()+
  theme(legend.position = "bottom") +
  labs(fill = 'With influential points') 

p2 = ggplot(mod_detail) +
  geom_point(aes(log_gdp,.fitted)) +
  geom_point(data = filter(mod_detail, name %in% c('Suriname', 'Angola', 'Botswana', 'Sudan', 'Gabon', 'Sierra Leone', 'Togo', 'Burundi')), aes(log_gdp,.fitted),col="red")

p3 = ggplot(mod_detail) +
  geom_point(aes(cpi,.fitted)) +
  geom_point(data = filter(mod_detail, name %in% c('Suriname', 'Angola', 'Botswana', 'Sudan', 'Gabon', 'Sierra Leone', 'Togo', 'Burundi')), aes(cpi,.fitted),col="red")

p4 = ggplot(mod_detail) +
  geom_point(aes(log_population,.fitted)) +
  geom_point(data = filter(mod_detail, name %in% c('Suriname', 'Angola', 'Botswana', 'Sudan', 'Gabon', 'Sierra Leone', 'Togo', 'Burundi')), aes(log_population,.fitted),col="red")

p5 = ggplot(mod_detail) +
  geom_point(aes(log_area,.fitted)) +
  geom_point(data = filter(mod_detail, name %in% c('Suriname', 'Angola', 'Botswana', 'Sudan', 'Gabon', 'Sierra Leone', 'Togo', 'Burundi')), aes(log_area,.fitted),col="red")

grid.arrange(p1, arrangeGrob(p2, p3, p4,p5, ncol=2), top = "Diagnostics for influential data points\n Top: World map of countries with influential data points. \n Bottom: Scatter plots of fitted value against each regressor. Red dots represent the infulential data points.", ncol=1, heights =c(2,1))
```


